---
title: "Developing Data Products Week 4 Assignment"
author: "Jessie J. Q"
date: "April 9, 2019"
output: html_document
---

## Synopsis

This assignment has two parts. The first part includes developing a Shiny application and the deployment of this application on Rstudio's server. The second part is to prepare a reproducible pitch presentation about this application.

## About this application

This application gives user an interactive way to find out the stock prices for Google, Apple, Facebook and Amazon in the past fourteen year. Users can choose company name, and the date range that they are interested in knowing and then click on the plot to see the price.

This application is bulit on the GAFA Stock Price dataset from Kaggle. Below is the link to this dataset.
https://www.kaggle.com/stexo92/gafa-stock-prices

## Data Understanding

GAFA (Google, Apple, Facebook, Amazon) stock prices until 20 April 2018.

Source: Yahoo Finance

Columns: 
1. Stock
2. Date
3. Open
4. High
5. Low
6. Close
7. Adj Close
8. Volume

## Data Preparation
1. Load the data
2. Check missing value. There is no missing value in this dataset.
3. Transform character and factor data into numeric format
4. Transform date from factor to date format
3. Plot the data to display relationship, density and distribution

```{r, include=FALSE, echo=TRUE, error=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(GGally)
library(DataExplorer)
```

```{r, include=TRUE, echo=TRUE}
gafa <- read.csv("C:/Users/JJQ/Documents/data/GAFA Stock Prices.csv", stringsAsFactors = FALSE)
str(gafa)
summary(is.na(gafa))
```

```{r, include=TRUE, echo=TRUE}
sub_gafa <- select(gafa, Open:Volume)
sub_gafa1 <- lapply(sub_gafa, function(x)(as.numeric(x)))
sub_gafa2 <- as.data.frame(sub_gafa1)

date <- as.Date(gafa$Date, '%d/%m/%Y')

gafa_stock <- cbind(gafa$Stock, date, sub_gafa2)
colnames(gafa_stock) <- c("Company", "Date", "Open", "High", "Low", "Price", "AdjClose", "Volume" )
str(gafa_stock)
head(gafa_stock)

```
### Subset dataframe based for each company
```{r, include=FALSE, echo=FALSE}
Google <- gafa_stock %>% filter(Company == "Google")
head(Google)
str(Google)

Amazon <- gafa_stock %>% filter(Company == "Amazon")
str(Amazon)

Apple <- gafa_stock %>% filter(Company == "Apple")
str(Apple)

Facebook <- gafa_stock %>% filter(Company == "Facebook")
str(Facebook)
```

### Plot distribution


```{r, include=TRUE, echo=TRUE}
plot_histogram(gafa_stock)

plot_density(gafa_stock)
```

### Plot correlation
```{r, include=TRUE, echo=TRUE}

ggplot(gafa_stock, aes(Date, Price, color = Company)) + geom_line()

ggcorr(gafa_stock, label = TRUE)
```


## Shiny Application

*** ui.R

```{r, include=FALSE, echo=FALSE}
library(shiny)

shinyUI(fluidPage(
  
  titlePanel("GAFA Stock Prices"),
  
  sidebarLayout(
    sidebarPanel(
      selectInput(inputId = "dataset",
                  label = "Choose a company:",
                  choices = c("Amazon", "Apple", "Facebook", "Google")),
      
      dateInput("date", "Date", min = 2004-08-18, max = 2018-04-20),
      
      numericInput(inputId = "obs",
                   label = "Number of observations to view:",
                   value = 10),
      
      checkboxInput("show_xlab", "Show/Hide X Axis Label", value = TRUE),
      checkboxInput("show_ylab", "Show/Hide Y Axis Label", value = TRUE) 
      
    ),

    # Show a plot of the generated distribution
    mainPanel(
       plotOutput("plot1"),
       tableOutput("view")
      
    )
  )
))


```


*** server.R

```{r, include=FALSE, echo=FALSE}
library(shiny)
library(ggplot2)
library(dplyr)

# Define server logic required to draw a histogram
shinyServer(function(input, output) {
  datasetInput <- reactive({
    switch(input$dataset,
           "Apple" = Apple,
           "Amazon" = Amazon,
           "Facebook" = Facebook,
           "Google" = Google)
  })
  
  output$summary <- renderPrint({
    dataset <- datasetInput()
    summary(dataset)
  })
   
  output$view <- renderTable({
    head(datasetInput(), n = input$obs)
  })
  
  output$plot1 <- renderPlot({
    
    g <- ggplot(gafa_stock, aes(Date, Price, color = Company)) + geom_line() + xlab("Date") + ylab("Price")
    print(g)
   
  })
 
  
})

```













